Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-06-22 R0V0.tex
> Done: Writing the example.

Consider the network composed of interconnected systems described by the equation
\begin{equation}\label{eq:example}
		\left\{\begin{array}{rcl}
			\dot{x}_i&=&\dfrac{a}{k+z_i}-bx_i+d(x_{i-1}-2x_i+x_{i+1})\\
			\dot{y}_i&=&\alpha x_i-\beta y_i\\
			\dot{z}_i&=&-\dfrac{\delta z_i}{k_M+z_i}+\gamma y_i+u_i\\
		\end{array}\right.
\end{equation}
where $a,b,d,k,k_M,\alpha,\beta,\gamma,\delta\in\mathbb{R}_{>0}$ are constant values, and $x_0:=x_1$ and $x_{N+1}=x_N$ for convenience.

System \eqref{eq:example} is a variation of the ``Goodwin model'' (introduced in \cite{Goodwin1965}) and considered in \cite{Aminzare2014a}. When $d=0$, this system is a generic model describing how persistent oscillations can be generated by an autoinhibitory gene circuit \cite[Section 7.3.1]{Ingalls2013}. The variable $x_i$ is the mRNA is translated into the enzyme $y_i$ which catalyses the production of the metabolite $z$. The metabolite $z$ supresses the transcription of the mRNA. When $d\neq0$, the composed network is interconnected throughout a diffusive term.

>>>>

Consider the network composed of interconnected systems described by the equation
\begin{equation}\label{eq:example}
		\left\{\begin{array}{rcl}
			\dot{x}_i&=&\dfrac{a}{k+z_i}-bx_i+d(x_{i-1}-2x_i+x_{i+1})\\
			\dot{y}_i&=&\alpha x_i-\beta y_i\\
			\dot{z}_i&=&-\dfrac{\delta z_i}{k_M+z_i}+\gamma y_i+u_i\\
		\end{array}\right.
\end{equation}
where $a,b,d,k,k_M,\alpha,\beta,\gamma,\delta\in\mathbb{R}_{>0}$ are constant values, and $x_0:=x_1$ and $x_{N+1}:=x_N$ for convenience.

System \eqref{eq:example} is a variation of the ``Goodwin model'' (introduced in \cite{Goodwin1965}) and it is also based on \cite{Aminzare2014a}. When $d=0$, this system is a generic model describing how persistent oscillations can be generated by an autoinhibitory gene circuit \cite[Section 7.3.1]{Ingalls2013}. The variable $x_i$ is the mRNA is translated into the enzyme $y_i$ which catalyses the production of the metabolite $z$. The metabolite $z$ supresses the transcription of the mRNA. When $d\neq0$, the composed network is interconnected throughout a diffusive term.
